Finding GENERAL Defect Prediction Models Within Hundreds of Software Projects

### 2020-04-17 response.tex

\response{Thank you for your comment, we forgot to include the unit for dataset size in Fig. 4 (Now Fig~\ref{fig:meta}) in the last  version. The unit for dataset size is number of rows for each dataset and it has been added into the figure as well.}

\review{(2.26) [Sec. 5] Why do you need a figure (Fig. 6) for two numbers?}

\response{Thank you for your comment, the Figure Figure 6 has been removed from this version. We have included Figure~\ref{fig:compare_time} which shows the time taken by traditional bellwether and GENERAL (without CFS and SMOTE) with increasing project community size. these two figures are important to showcase the scalability of the new bellwether method aka GENERAL.}

@@

\section*{Reviewer 3}

\response{Thank you very much for your detailed review. As we said to the associated editor, the prior draft  assumed that the core motivation for this work was widely known and accepted in the community. That was a mistake so this draft completely rewrites the Introduction to include much more background information on the presence of the problem studied here. Also, thanks to your feedback, 
we have made some additional corrections, clarifications, and revisions, as directed by your comments. Please note that to assist in your review, we refer to specific locations of each of the changes using the notation \respto{3-XX}.}

\review{(3.1)The manuscript introduces a new approach GENERAL, which just applies hierarchical clustering. As far as I understand, hierarchical clustering is a well-known, standard, and largely-evaluated clustering algorithm. I don’t really see the need to re brand it with a new name. What is the difference between GENERAL and hierarchical clustering other than the GENERAL is applied to defect prediction?}

@@

\review{(3.2) Figure 1 “shows a hypothetical cost comparison in AWS between standard bellwether and GENERAL.” If the Figure is hypothetical, why do we need it? Is it based on real data? As far as I understand, the plot is merely speculation and as such is should be included in scientific papers.}

\response{Thank you for your comments.   We have removed all the hypothetical graphs and added data from actual experiment in this version of manuscript.}

\review{(3.3) I am also very concerned about the (unproven) assumption that we can make conclusions that hold across multiple projects. While the dataset includes 700 projects, we have no information about the project, the domain applications, critically (e.g., safety-critical systems vs. generic open-source Java libraries). I don’t really see how a model trained on dozens of open-source apache libraries can be applied to robotics, medical systems, etc. Note that for the latter domains, testing, requirements engineering, and maintenance are different and have peculiar standards (e.g., MC/CD coverage for automotive systems vs. statement coverage for non-critical systems).  }

\response{We are not very clear on this comment.
In our view,   bellwethers are a method that has been demonstrated useful in many domains. 
As shown by our precision, recall, false alarm, etc results, this paper
shows that we can make general conclusions across this space of projects.}

\response{Also, in other papers\cite{krishna2018bellwethers,krishna2017simpler, nair19a, krishna16, krishna16a}, we have shown that
 bellwethers have worked to generate:
\begin{itemize}
\item
configurations for cloud-based tools~\cite{krishna2019whence}
(this recently got accepted to TSE);
\item 
effort estimation;
\item
predicting Github issue close time, 
\item
code bad smell detection.
\end{itemize}
}

\response{
However, and this is the point of this paper, the existing  method does not scale to large data sets. Hence, this paper.}

@@

\review{(3.8) As mentioned in one of my comments above, the script seeks to model generalizability looking at the number of projects (and size) as solely dimension to look at. But what about the quality attributes, such as the application domain? What are the application domains of the projects? Are there only open-source projects? How about industrial projects, including the financial, automotive, and robotics sectors? How many web and mobile applications are in the sample? Does the dataset cover these domains? If not, how can we claim that 700 projects can bring us to generalizability?}

\response{Please see comment 3.3 and 3.6}

\review{(3.9) Furthermore, the dataset looks quite strange to me. Looking at the defect distributions (left-most boxplot in Figure 4), I do see that 75\% of the projects (the last quartile) have more than 60\% of defective modules (classes/methods?). Some have a defective percentage above 80\%. Do we need machine learning to predict defects in projects where almost all modules are defectives? In these projects, a simple, constant classifier would work the best. The results also show this for ZeroR in Section 5.}

\response{Thank you for your comment. In this study, ZeroR is a method where we predict everything as majority class. This effectively means for any project where in the training data majority of the modules are defective, all test data will be predicted as defective (increasing pf and lower precision) and vice-versa if majority of the modules are non-defective. The dataset we are working with more then 50\% of the projects has less than 50\% defective modules. So ZeroR will detect no defects in all these projects (Figure~\ref{fig:Statistical} show the median recall is zero precisely for this reason). This is the reason we can't use ZeroR as a recommended model.
We have added notes on that in \S\ref{sec:isk} and \citeresp{3-9}.}

@@

\review{(3.10) Throughout the manuscript, the complexity of GENERAL is suggested to be $O(m * (N/m)^2)$. But there is proof about the complexity whatsoever. Either the manuscript cites proofs from existing papers (e.g., related work on hierarchical clustering) or provides a complete proof (perhaps in an appendix).}

\response{Thank you for your comment, we didn't included detailed analysis of complexity of our method in the last manuscript. We have added much details and an step by step analysis \citeresp{3-10} of complexity of the algorithm shown in Fig~\ref{fig:Pseudo-code}.}

\review{(3.11a) All the results are summarized in one single table (Figure 7), which shows the mean and the standard deviation of five evaluation metrics, as well as the rank of the statistical tests. There are two problems in aggregating the data in this way: (1)I am not sure that the arithmetic mean and the standard deviation are the appropriate metrics to use. Are the data normally distributed? Do we have many outliers? Perhaps, median and IQR are more appropriate as they are less affected by outliers.}

\response{Thank you for your comment, you are quite correct. We used arithmetic mean and standard deviation as our metrics to showcase our result in the last manuscript, which may be affected by outliers and skew the results. In this manuscript, we have replaced arithmetic mean and standard deviation with median and IQR in Figure~\ref{fig:Statistical}.}

@@

\review{(3.11b)Maybe, the boxplots would be the most appropriate way to show the distributions. (2)The average across 700 projects makes little sense and hides what happens in each project. What happens per project? In how many projects does GENERAL performs better than the standard bellwether learner?}

\response{Thank you for your comments. The Fig~\ref{fig:Statistical} is a form of box-plot, where the black dot represents the median and the spread of the black line represents the 25th and 75th percentile of the data. Also note that the ranks we offer in that figure (in the left-hand-column) are generated via non-parametric statistics
(bootstrap and the A12 effect size test) that do not assume Gaussian.}

@@

\review{(3.12) Section 5 contains the following recommendation “As to ZeroR, we cannot recommend that approach. While ZeroR makes few mistakes (low ifas and low pfs), it scores badly on other measures (very low recalls and popt(20).” This argument does not convince me as ZeroR gets the best results for two metrics (as far as I understand). Please elaborate more on why we cannot use ZeroR. Besides, ZeroR may work relatively well because of projects with a very large number of defects. Perhaps, some in-depth analysis of the correlation between defect distributions and performances of the models would be very useful.}

\response{Thank you for your comments, in the last manuscript we did not properly explained why the model ZeroR can not be recommend. We have updated the Figure~\ref{fig:Statistical} to replace arithmetic mean and standard deviation with median and IQR. Figure~\ref{fig:Statistical} shows ZeroR model has a median recall and pf of zero with IQR diff between 75th and 25th percentile as 100. This result signifies the model either predicts everything as defective or non-defective. This is because ZeroR is a method where we predict everything as majority class. This effectively means for any project where in the training data majority of the modules are defective, all test data will be predicted as defective (increasing pf and lower precision) and vice-versa if majority of the modules are non-defective. In the dataset that we have used more then 50\% of the projects has less than 50\% defective modules, thus in result the median recall, precision and pf is zero.}

@@

\review{(3.13) Section 5 (RQ3) ends with two recommendations about critical and non-critical systems. However, I could not find any analysis that can support these recommendations. I also queried the paper looking for the keywords “critical systems,” but I could not find anything except the recommendation with these keywords. To address this, there are only two mutually exclusive solutions: either remove the recommendations or add in-depth analysis that can provide empirical evidence to the claims.}

\response{Thank you for your valuable comments, the text for section~\ref{sec:rq6} was indeed confusing. We have removed that confusing terminology.}
